A Bayesian Framework for Learning Regular Expressions

### 2012-12-08 paper/paper.tex
i hope this is actually fixed

% 
% Annual Cognitive Science Conference Format

\documentclass[10pt,letterpaper]{article}

\usepackage{mathtools}
\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}

\title{A Bayesian Framework for Learning Regular Expressions}

\author{{\large \bf{P. Thomas Barthelemy} (bartho@stanford.edu)} \\
  Department of Computer Science, 353 Serra Mall \\
  Stanford, CA 94305 USA
  \AND {\large \bf Nicholas Borg (nickborg@stanford.edu)} \\
  Symbolic Systems Program, Margaret Jacks Hall \\
  Stanford, CA 94305 USA}

\begin{document}

\maketitle

\begin{abstract}
Regular expressions are used to define a set of strings that match a certain pattern. In the following experiment, we posit that the means by which humans judge similarity of words can be represented by a method of inference using regular expressions. In short, there is a tradeoff of generality and specificity that allows for a selection of an optimal regular expression to categorize a list of input strings.

\textbf{Keywords:} 
Model inference, regular expression.
\end{abstract}

\section{Overview and Motivation}
Understanding the human ability to find structure in data is integral to both cognitive psychology and artificial intelligence. In recent years, a number of studies have shown that human inference across a number of tasks may be Bayesian at some level of analysis. 
Inspired by the treatment of the number game in \citeA{tenenbaum1999bayesian}, we propose a regular expression game as follows: Given a set $S$ of input strings drawn from a language $L$, what is the likelihood that a new string $s$ is in $L$. Playing such a game requires inferring the rules that govern $L$ from $S$. Noting that humans perform this task  with success on a daily basis in writing regular expressions to process string data, we considered the hypothesis that human inference of regular expressions is at some level Bayesian.

In doing so, we first generated a Bayesian model that, given a set of input strings $S$, generated a regular expression that describes $S$ with the highest posterior probability. This model is discussed in the first part of this paper. We then conducted a behavioral experiment in which subjects were asked whether or not a given string $s$ fits with a set of strings $S$. We compare the result of that experiment with results generated given an extension of our model.

\section{Description of the Model}

%\subsection{Balancing Generality with Specificity}
Our model has two parts: We generate a set of regular expressions which describe a set of input stings $S$, and we find the regular expression in that set with the highest posterior probability. The posterior probability is proportional to the product of the hypothesis' prior probability and its likelihood.
\begin{align*}
	p(h|S) \propto p(h) p(S|h)
\end{align*}
Below, we define the prior probability such that our model biases smaller hypotheses, and the likelihood of generating a given hypothesis is inversely proportional to its cost. Our model aims to balance generality with specificity. For example, given ``ABC, ABD", we wish to favor the regex $AB(C|D)$ over ``?*", which is less likely given the size principle. At the same time, given ``ABA", ``ABC", ``ABD", ``ABE", ``ABF", we may wish to favor `AB?' over  `$AB(A|C|D|E|F)$'

\subsection{Representation of Hypotheses}
Regular expressions are equivalent to deterministic finite automata (DFA).\footnote{See the Appendix for a brief summary of our regex notation.} Because DFA are often easier to reason with, we use them to represent regular expressions in our model (See Fig ~\ref{readin} for an example DFA.)

Further, we define the probability with which a DFA would stop generating a string at a start state . For instance, given the regular expression \verb!a*!, we would need to define the probability of generating strings \verb!a!, \verb!aa!, \verb!aaa!, etc.

In this sense, our DFA is similar to a probabilistic automaton, although the acceptance criteria is $\tau=0$, so the languages represented by our DFA are still regular. [Citation]. A second difference is that there is no concept of stopping string generation in probabilistic automaton.

% TODO: explain character scope!

\subsection{Generating Hypotheses}
The hypothesis space is initiated with the base hypothesis, the term applied to a DFA that accepts strictly the input strings. We begin generating a series of consecutive states, where the transition between the first state and the second state is governed by the first letter of the first string, the transition between the second and the third is governend by the the second letter, and so on. For each additional string, if the first i characters overlap with those of any of the first i characters of one previous string but differ in the $i+1$th, we add no new states to the DFA until the transition between the i-1th state and the ith state. We then generate new states for the remaining characters of the string. See Figure~\ref{readin} for an exapmle of the first hypothesis generated from a set $S$.
  \begin{figure}[ht]
\begin{center}
\begin{align*}
\includegraphics[scale=0.4]{readin.png}
\end{align*}
\end{center}
\caption{An example base hypothesis DFA generated from the strings `ababb' and `abbab'. Note that the two strings share the first two states, but that the fifth and tenth are distinct.} 
\label{readin}
\end{figure}

Next, hypotheses are added to the hypothesis space through two processes of generalization: merging and applying wildcards.

\subsubsection{Merging} Merging is the process of combining states of a DFA. The newly create state has all incoming and outgoing transitions of its predecessors. Thus, the DFA will continue to accept the same set of strings as the original DFA. However, the DFA will often accept more strings after merging, thus merging states results in a more generalized DFA.

If merging is continued, the DFA will eventually have only one state with all transitions leading to itself. Such a state accepts all strings containing only zero or more of the original characters. A series of merges are illustrated in Figure~\ref{merge-figure}.

\begin{figure}[ht]
\begin{center}
\begin{align*}
\text{(a)}\includegraphics[scale=0.4]{merge-0.png}
&\text{(b)}\includegraphics[scale=0.4]{merge-1.png}
&\text{(c)}\includegraphics[scale=0.4]{merge-2.png}
\end{align*}
\end{center}
\caption{An example of state merging. The DFA starts at state 0 and accepts only at the shaded states. The base hypothesis accepts ``b'' and ``ab'' (a). After merging states 0 and 2, the next DFA accepts an infinite set of strings (b). Finally, the merge of states 0 and 1 forces the merge of state 0 and 3 to maintain one unique outbound transition for any state and character (c).} 
\label{merge-figure}
\end{figure}

% TODO: mention anti-unification

\subsubsection{Wildcards} Wildcards generalize the DFA by extending state transitions to apply to a class of characters. Figure~\ref{wildcard-figure} illustrates an example of this.

\begin{figure}[ht]
\begin{center}
\begin{align*}
\text{(a)}\includegraphics[scale=0.4]{wildcard-0.png}
&\text{(b)}\includegraphics[scale=0.4]{wildcard-1.png}
\end{align*}
\end{center}
\caption{An example of inserting a wildcard, ``A'', which represents any character. Replacing a wildcard for one of the outbound transitions of state 0 has forced a merge of states 1 and 3.} 
\label{wildcard-figure}
\end{figure}

\subsubsection{Enforcing Determinism} Merging states and replacing transitions with wildcards can allow one state to have non-unique outbound transitions. However, this turns our representation into a nondeterministic finite automaton (NFA) instead of a DFA. Both are equivalent, but the latter afford easier manipulation for our experiment. Thus, to convert the NFA back to a DFA, we use the subset construction, the effect of which is illustrated in both Figure~\ref{merge-figure} and Figure~\ref{wildcard-figure}.

\subsection{Searching the Hypothesis Space} The number of hypotheses grows quickly with the number of states in the base hypothesis. As a lower bound, the number of hypotheses is at least as large as the number of possible starting nodes. Because the starting node could be merged with any subset of the remaining $n-1$ nodes in the DFA, there are $2^{n-1}=\Omega(2^n)$ possible start states. Thus, the hypothesis space is at least exponential in the number of starting nodes in the regular expression.

Similarly, the number of possible regex variants created by simply replacing transitions with wildcards is given by $2^m$ where $m$ is the number of transitions. Thus, simply modifying expressions to include wildcards is also exponential.

An upper bound for the complexity of model merging is much more extreme. Performing subset construction for an NFA with $n$ states can produce, in the worst case, a DFA with $2^n$ states. Assuming that any subset of these states also produces a valid DFA, we can have at most $2^{2^n-1}$ DFA.
% \footnote{See the Appendix for detailed sizing of the hypothesis space.} Actually, this seems inaccurate.

We resolve this issue by performing beam search. In beam first, we perform breadth first search, but for any given depth of the search tree, we only consider children of the $m$ most promising hypotheses. In our case, the most promising hypotheses were defined as those with the highest posterior probability. (For a more detailed discussion of Beam Search, see \cite{HwangStuhlmullerGoodman2011}

\section{Inference with DFA}
The posterior probability for a DFA as a hypothesis is given by the following.
\begin{align*}
	p(h|S) \propto p(S|h)p(h)
\end{align*}
Thus, inferring the best DFA given a set of input strings was essentially a problem in balancing simplicity with conservation of belief. That is, DFA were biased a priori for being simpler, but simpler DFA tended to accept more strings.

\subsection{Prior Probability}
We assigned the prior probability to the hypotheses (i.e. regexes) based on the size of the DFA and the number of transitions. In the following equation, $|S|$ is the number of states in the DFA and $|T|$ is the number of tranisitons in the DFA, where a wildcard counts as only one transition. 
\begin{align*}
	P(h) \propto e^{-\alpha|S| - \beta|T|}
\end{align*}
Thus, we have biased smaller DFA that use wildcards instead of literal characters. [cite Program Merging model]

\subsection{Likelihood}
To define the likelihood of producing certain strings, we turn a DFA into a generative automaton that has a probability of generating a given string. Letting the input strings be independent, the probability of generating strings $S$ is equal to the product of the probabilities of generating each string.
\begin{align*}
	p(S) = \prod_{s \in S} p(s)
\end{align*}

Let the $s$ be the concatenation of characters $a_1a_2...a_n$. We define the probability of generating a string as the product of the probability of generating the letters in sequence $p(a_1a_2...a_n)$ and the product of stopping the string generation on an accept state $p(\text{stop})$.
\begin{align*}
	p(s) = p(a_1a_2...a_n)p(\text{stop})
\end{align*}

We define the probability of generating the characters as the product of the probabilities of making each state transition over each state.
\begin{align*}
	p(a_1a_2 ... a_n) = \prod_{i=1}^{n}p(\delta(r_i, a_{i+1}))
\end{align*}
where $r_i$ is the state reached after the first $i-1$ characters, and $r_1$ is the start state.

To simplify inference, we assume uniform probability over all possible state transitions. Formally, the probability of making a state transition is given by:
\begin{align*}
	p(\delta(r_i, a_{i+1})) &= \frac{1}{\sum_{a\in A} 1\{\delta(r_i, a)\}}
\end{align*}
Notice that the denominator counts the number of characters for which a transition is defined. In the case of a wildcard, the transition is defined for all 26 letters.

For the cases in which a string may alternatively be accepted or continue, one must assign a probability for accepting or continuing the string. For instance, consider the DFA in part (c) of Figure~\ref{merge-figure}. The DFA may generate the empty string, \verb!E!, or it may generate any arbitrary string with \verb!a! and \verb!b!, like \verb!ababbba!. We define the probability of stopping at a given string to be a fixed value $\tau$. This makes shorter strings more likely to be generated.

Instead of leaving $\tau$ as a parameter of the model, we assume a uniform prior over the parameter and marginalize it when calculating the likelihood of a string. So, let $b$ be the number of times the DFA skipped an accept state before accepting. That is, $b$ is given by the equation below, where $F$ is the set of accept states.
\begin{align*}
	b = \sum_{i=1}^{n-1} 1 \{ r_i \in F\}
\end{align*}

% TODO: Cite this

The probability of stopping at an accept state is given by the equation below. The condition $\exists a : \delta(r_n, a)$ indicates that there is an outbound transition for the accept state of the string.
\begin{align*}
	p(\text{stop}) &= \left\{
		\begin{array}{rl}
		\tau (1-\tau)^b & r_n \in F \wedge \exists a : \delta(r_n, a)
		\\ (1-\tau)^b & r_n \in F \wedge \not \exists a : \delta(r_n, a)
		\\ 0 & \text{otherwise}
		\end{array}
		\right.
\end{align*}

Marginalizing over all possible values of $\tau$, we have:
\begin{align*}
	\int_0^1 \tau (1-\tau)^b &= \frac{1}{b^2+3b+1}
	\\ \int_0^1 (1-\tau)^b &= \frac{1}{b+1}
\end{align*}

Our equation for $p(\text{stop})$ is thus:
\begin{align*}
	p(\text{stop}) &= \left\{
		\begin{array}{rl}
		\frac{1}{b^2+3b+1} & \in F \wedge \exists a : \delta(r_n, a)
		\\ \frac{1}{b+1} & \in F \wedge \not \exists a : \delta(r_n, a)
		\\ 0 & \text{otherwise}
		\end{array}
		\right.
\end{align*}

\section{Experiment Design and Model Fitting}
Having generated the above Bayesian model for selection of the regular expression with the highest posterior probability, we then conducted a behavioral experiment.  41 subjects (Median age 34, std-dev 13.3) were surveyed on Amazon Mechanical Turk. Two groups (one of twenty, one of 21) were presented with 10 yes or no questions in which they were asked to determine whether a given string `fit' with a list of strings. A sample question was as follows: \\
\begin{center}Given the list:

\textbf{yyyt \\
yt \\
yyyt \\
yyyt \\ 
yt}

Does \textbf{yyt} fit?
\end{center}

The experimental data served two purposes. Using the responses to four out of 23 questions, we set the parameters for alpha and beta. We then used the remaining questions to test our model's performance in a regex game as shown below.

\subsection{Parameter Fitting}
Because the role of $\beta$ had the effect of biasing models with fewer transitions, it also had a tendency to bias regular expressions with fewer states. For instance, the $\beta$ term would prefer the regular expression \verb!a*! over \verb!aaaa!. Thus, this term was fitted before fitting the $\alpha$ term.

To fit the $\beta$ term, we observed experiments that would indicate the transition point between a preference for generality over specificity for wildcard-based experiments (e.g. the first two experiments outlined in Table~\ref{parameter-table}). Utilizing the fact that increasing the ratio of repeated strings to new strings decreases the likelihood of a wildcard, and decreasing the length of the sample strings would increases the likelihood of a wildcard, the first two experiments suggest a decision point. That is, if the DFA model is a valid representation of the subjects' responses, then the $\beta$ term should be between $3$ and $5$. For further experimentation, we fixed it at $4$.

Fitting the $\alpha$ term was less clear. In particular, the desired behavior was easily observed with $\alpha=0,\beta=4$. However, a term of $\alpha=1$ was used to bias hypotheses with fewer states given the same number of transitions.

% TODO: move this?
\begin{table}[!ht]
\begin{center} 
\caption{Parameter fitting experiments} 
\label{parameter-table} 
\vskip 0.12in
\begin{tabular}{llll} 
\hline
Input  & Test & Subject Accept & Model Accept
% \\ \hline
% bhi, bhw, bhi, & bho & 30\% & $\beta < 14$
% \\ bhw, bhw
\\ \hline
efg, hfg, ifg & ffg & 45\% & $\beta > 3$
\\ \hline
glts, elts, glts, & ilts & 70\% & $\beta > 5$
\\ flts
\\ \hline
ab, abb & abbb & 90\% & $\alpha = 0, \beta = 4$
\\ \hline
ao, aoo, aooo & aoooo & 80\% & $\alpha = 0, \beta=4$
\\ \hline
\end{tabular} 
\end{center} 
\end{table}

\subsection{The Regex Game}
Given the fitted model, we then considered the following task:

Given a language $\mathcal{L}$, a set of regular expressions $\mathcal{H}$ (where these are candidates for $\mathcal{L}$), a set of strings drawn $S$ from $\mathcal{L}$, and a string $s$, we define

\begin{align*}
	p(s \in \mathcal{L} | S \subseteq {L}) = \sum_{h \in \mathcal{H}} 1 (s \in h) p(h|S)
\end{align*}

For human participants, because the hypothesis is unobserved, we take $p(s \in \mathcal{L} | S \subseteq {L}) $ to be the average acceptance of a test string given a set $S$.

In our model, we consider $\mathcal{H}$ to be the set of all hypotheses generated in our model.

\section{Results and Discussion}
Figure 3 shows the comparison between our model and the human subject data.

\begin{figure}[ht]
\begin{center}
\begin{align*}
\includegraphics[scale=0.6]{results.png}
\end{align*}
\end{center}
\caption{Chart showing  $p(s \in \mathcal{L} | S \subseteq {L}) $. Human subject data is in red, model data is in blue. $R$ = .75} 
\label{-figure}
\end{figure}

We note that subjects completed the 10 or 11 question survey on average in around three minutes. It remains unclear if more standardized results would have emerged in certain cases if subjects had taken more time with the task. In addition, more fine grained results may have been obtained if we had instead allowed users to bet certain amounts on whether or not a test string was in $S$.

We note that in cases 1 (S = \{'yyyt', `yt', `yyyt', `yyyt', `yt'\}, s= `yyyyyt' ), 4( S = \{jojojojo', `jojojojo', `jojojojo'\}, s = jojo), and 6 (s =  tw,  S = \{'twtwtw', `twtwtw', `twtwtw'\}), it is clear that the model weighs a smaller number of transitions greater than human subjects do. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases. This suggests that our model's parameter $\beta$ may in fact be better represented by more than one variable in human decision making.

We also observe that in such cases, there was a relatively small set of probable hypotheses, and that any favoring of smaller hypotheses was magnified by this fact. 
\section{Conclusion and Future Work}

Despite the number of ways in which our model might be improved mentioned above,  it remains highly implausible that the brain generates its set of candidate hypotheses by ever considering even $2^n$ hypotheses in the first level of beam search we perform, much less far more than that. Doing so would be highly inefficient: the number of implausible hypotheses generated would in most cases be far greater than the number of `good' hypotheses. Far more plausible a priori is the hypothesis that the brain uses of number of heuristics to generate a certain set of candidate hypothesis, and then uses some process analogous to Bayesian inference to select among those hypotheses. To shed light on how this hypothesis selection process may occur, we designed an experiment in which candidates chose among a number of possible rules to explain a set of strings S, but have yet to gather enough data to reach any significant conclusions.

Further experiments could be conducted to determine what heuristics may be at work in the hypothesis generation process. For any set of candidate heuristics, it will remain to be determined whether or not such heuristics are at some point learned. Clearly some semantic considerations are at work in human pattern recognition on strings: cat and mat but not qat are meaningful english words; `ao' and `eo' and `io' begin with vowels unlike `xo'. (This experiment was designed to avoid such candidate hypotheses.)

>>>>

<!DOCTYPE html>
<html>
  <head prefix="og: http://ogp.me/ns# fb: http://ogp.me/ns/fb# githubog: http://ogp.me/ns/fb/githubog#">
    <meta charset='utf-8'>
    <meta http-equiv="X-UA-Compatible" content="IE=edge">
        <title>PSYCH204_Project/paper/paper.tex at master · ptbarthelemy/PSYCH204_Project</title>
    <link rel="search" type="application/opensearchdescription+xml" href="/opensearch.xml" title="GitHub" />
    <link rel="fluid-icon" href="https://github.com/fluidicon.png" title="GitHub" />
    <link rel="apple-touch-icon-precomposed" sizes="57x57" href="apple-touch-icon-114.png" />
    <link rel="apple-touch-icon-precomposed" sizes="114x114" href="apple-touch-icon-114.png" />
    <link rel="apple-touch-icon-precomposed" sizes="72x72" href="apple-touch-icon-144.png" />
    <link rel="apple-touch-icon-precomposed" sizes="144x144" href="apple-touch-icon-144.png" />
    <meta name="msapplication-TileImage" content="/windows-tile.png">
    <meta name="msapplication-TileColor" content="#ffffff">

    <link rel="icon" type="image/x-icon" href="/favicon.ico" />

    <meta content="authenticity_token" name="csrf-param" />
<meta content="WJuSSAjRdnVShD8r6DrOrsEgL/AxT6yLvH+B4+7oqpY=" name="csrf-token" />

    <link href="https://a248.e.akamai.net/assets.github.com/assets/github-a2a679dc329adac0ae0f3c8a55962cd292b6bb2e.css" media="screen" rel="stylesheet" type="text/css" />
    <link href="https://a248.e.akamai.net/assets.github.com/assets/github2-ddbc9d73271e204f76d48b6abb07e8791f16a0d5.css" media="screen" rel="stylesheet" type="text/css" />

    <script src="https://a248.e.akamai.net/assets.github.com/assets/frameworks-eee761b9d5e06efb064aaaf528c44ef8e1601e71.js" type="text/javascript"></script>
    <script src="https://a248.e.akamai.net/assets.github.com/assets/github-9dff60969c141f6060b5c427c34662424aefe349.js" type="text/javascript"></script>

      <link rel='permalink' href='/ptbarthelemy/PSYCH204_Project/blob/4f0d202c1ba791661a94da0e3af58abe72221df3/paper/paper.tex'>
    <meta property="og:title" content="PSYCH204_Project"/>
    <meta property="og:type" content="githubog:gitrepository"/>
    <meta property="og:url" content="https://github.com/ptbarthelemy/PSYCH204_Project"/>
    <meta property="og:image" content="https://secure.gravatar.com/avatar/2f3bac31ff97773344886e6ba59e1d49?s=420&amp;d=https://a248.e.akamai.net/assets.github.com%2Fimages%2Fgravatars%2Fgravatar-user-420.png"/>
    <meta property="og:site_name" content="GitHub"/>
    <meta property="og:description" content="Contribute to PSYCH204_Project development by creating an account on GitHub."/>

    <meta name="description" content="Contribute to PSYCH204_Project development by creating an account on GitHub." />

  <link href="https://github.com/ptbarthelemy/PSYCH204_Project/commits/master.atom" rel="alternate" title="Recent Commits to PSYCH204_Project:master" type="application/atom+xml" />

  </head>

  <body class="logged_in page-blob macintosh vis-public env-production ">
    <div id="wrapper">

        <div class="header header-logged-in true">
          <div class="container clearfix">

            <a class="header-logo-blacktocat" href="https://github.com/">
  <span class="mega-icon mega-icon-blacktocat"></span>
</a>

            <div class="divider-vertical"></div>

              <a href="/notifications" class="notification-indicator tooltipped downwards" title="You have no unread notifications">
    <span class="mail-status all-read"></span>
  </a>
  <div class="divider-vertical"></div>

  <div class="topsearch command-bar-activated">
    <form accept-charset="UTF-8" action="/search" class="command_bar_form" id="top_search_form" method="get">
  <a href="/search/advanced" class="advanced-search tooltipped downwards command-bar-search" id="advanced_search" title="Advanced search"><span class="mini-icon mini-icon-advanced-search "></span></a>

  <input type="text" name="q" id="command-bar" placeholder="Search or type a command" tabindex="1" data-username="nickborg" autocapitalize="off">

  <span class="mini-icon help tooltipped downwards" title="Show command bar help">
    <span class="mini-icon mini-icon-help"></span>
  </span>

  <input type="hidden" name="ref" value="commandbar">

  <div class="divider-vertical"></div>
</form>

    <ul class="top-nav">
        <li class="explore"><a href="https://github.com/explore">Explore</a></li>
        <li><a href="https://gist.github.com">Gist</a></li>
        <li><a href="/blog">Blog</a></li>
      <li><a href="http://help.github.com">Help</a></li>
    </ul>
  </div>

    <ul id="user-links">
      <li>
        <a href="https://github.com/nickborg" class="name">
          <img height="20" src="https://secure.gravatar.com/avatar/4c214ec0d06de350672ade1973246dd8?s=140&amp;d=https://a248.e.akamai.net/assets.github.com%2Fimages%2Fgravatars%2Fgravatar-user-420.png" width="20" /> nickborg
        </a>
      </li>
      <li>
        <a href="/new" id="new_repo" class="tooltipped downwards" title="Create a new repo">
          <span class="mini-icon mini-icon-create"></span>
        </a>
      </li>
      <li>
        <a href="/settings/profile" id="account_settings"
          class="tooltipped downwards"
          title="Account settings ">
          <span class="mini-icon mini-icon-account-settings"></span>
        </a>
      </li>
      <li>
          <a href="/logout" data-method="post" id="logout" class="tooltipped downwards" title="Sign out">
            <span class="mini-icon mini-icon-logout"></span>
          </a>
      </li>
    </ul>

          </div>
        </div>

            <div class="site hfeed" itemscope itemtype="http://schema.org/WebPage">
      <div class="hentry">

        <div class="pagehead repohead instapaper_ignore readability-menu">
          <div class="container">
            <div class="title-actions-bar">

                  <ul class="pagehead-actions">
          <li class="nspr">
            <a href="/ptbarthelemy/PSYCH204_Project/pull/new/master" class="minibutton btn-pull-request" icon_class="mini-icon-pull-request"><span class="mini-icon mini-icon-pull-request"></span>Pull Request</a>
          </li>

          <li class="subscription">
              <form accept-charset="UTF-8" action="/notifications/subscribe" data-autosubmit="true" data-remote="true" method="post"><div style="margin:0;padding:0;display:inline"><input name="authenticity_token" type="hidden" value="WJuSSAjRdnVShD8r6DrOrsEgL/AxT6yLvH+B4+7oqpY=" /></div>  <input id="repository_id" name="repository_id" type="hidden" value="6767293" />
  <div class="context-menu-container js-menu-container js-context-menu">
    <span class="minibutton switcher bigger js-menu-target">
      <span class="js-context-button">
          <span class="mini-icon mini-icon-unwatch"></span>Unwatch
      </span>
    </span>

    <div class="context-pane js-menu-content">
      <a href="#" class="close js-menu-close"><span class="mini-icon mini-icon-remove-close"></span></a>
      <div class="context-title">Notification status</div>

      <div class="context-body pane-selector">
        <ul class="js-navigation-container">
          <li class="selector-item js-navigation-item js-navigation-target ">
            <span class="mini-icon mini-icon-confirm"></span>
            <label>
              <input id="do_included" name="do" type="radio" value="included" />
              <h4>Not watching</h4>
              <p>You will only receive notifications when you participate or are mentioned.</p>
            </label>
            <span class="context-button-text js-context-button-text">
              <span class="mini-icon mini-icon-watching"></span>
              Watch
            </span>
          </li>
          <li class="selector-item js-navigation-item js-navigation-target selected">
            <span class="mini-icon mini-icon-confirm"></span>
            <label>
              <input checked="checked" id="do_subscribed" name="do" type="radio" value="subscribed" />
              <h4>Watching</h4>
              <p>You will receive all notifications for this repository.</p>
            </label>
            <span class="context-button-text js-context-button-text">
              <span class="mini-icon mini-icon-unwatch"></span>
              Unwatch
            </span>
          </li>
          <li class="selector-item js-navigation-item js-navigation-target ">
            <span class="mini-icon mini-icon-confirm"></span>
            <label>
              <input id="do_ignore" name="do" type="radio" value="ignore" />
              <h4>Ignored</h4>
              <p>You will not receive notifications for this repository.</p>
            </label>
            <span class="context-button-text js-context-button-text">
              <span class="mini-icon mini-icon-mute"></span>
              Stop ignoring
            </span>
          </li>
        </ul>
      </div>
    </div>
  </div>
</form>
          </li>

          <li class="js-toggler-container js-social-container starring-container ">
            <a href="/ptbarthelemy/PSYCH204_Project/unstar" class="minibutton js-toggler-target starred" data-remote="true" data-method="post" rel="nofollow">
              <span class="mini-icon mini-icon-star"></span>Unstar
            </a><a href="/ptbarthelemy/PSYCH204_Project/star" class="minibutton js-toggler-target unstarred" data-remote="true" data-method="post" rel="nofollow">
              <span class="mini-icon mini-icon-star"></span>Star
            </a><a class="social-count js-social-count" href="/ptbarthelemy/PSYCH204_Project/stargazers">0</a>
          </li>

              <li><a href="/ptbarthelemy/PSYCH204_Project/fork" class="minibutton js-toggler-target fork-button lighter" rel="nofollow" data-method="post"><span class="mini-icon mini-icon-fork"></span>Fork</a><a href="/ptbarthelemy/PSYCH204_Project/network" class="social-count">1</a>
              </li>

    </ul>

              <h1 itemscope itemtype="http://data-vocabulary.org/Breadcrumb" class="entry-title public">
                <span class="repo-label"><span>public</span></span>
                <span class="mega-icon mega-icon-public-repo"></span>
                <span class="author vcard">
                  <a href="/ptbarthelemy" class="url fn" itemprop="url" rel="author">
                  <span itemprop="title">ptbarthelemy</span>
                  </a></span> /
                <strong><a href="/ptbarthelemy/PSYCH204_Project" class="js-current-repository">PSYCH204_Project</a></strong>
              </h1>
            </div>

  <ul class="tabs">
    <li><a href="/ptbarthelemy/PSYCH204_Project" class="selected" highlight="repo_sourcerepo_downloadsrepo_commitsrepo_tagsrepo_branches">Code</a></li>
    <li><a href="/ptbarthelemy/PSYCH204_Project/network" highlight="repo_network">Network</a></li>
    <li><a href="/ptbarthelemy/PSYCH204_Project/pulls" highlight="repo_pulls">Pull Requests <span class='counter'>0</span></a></li>

      <li><a href="/ptbarthelemy/PSYCH204_Project/issues" highlight="repo_issues">Issues <span class='counter'>0</span></a></li>

      <li><a href="/ptbarthelemy/PSYCH204_Project/wiki" highlight="repo_wiki">Wiki</a></li>

    <li><a href="/ptbarthelemy/PSYCH204_Project/graphs" highlight="repo_graphsrepo_contributors">Graphs</a></li>

  </ul>

<div class="tabnav">

  <span class="tabnav-right">
    <ul class="tabnav-tabs">
      <li><a href="/ptbarthelemy/PSYCH204_Project/tags" class="tabnav-tab" highlight="repo_tags">Tags <span class="counter blank">0</span></a></li>
      <li><a href="/ptbarthelemy/PSYCH204_Project/downloads" class="tabnav-tab" highlight="repo_downloads">Downloads <span class="counter blank">0</span></a></li>
    </ul>

  </span>

  <div class="tabnav-widget scope">

    <div class="context-menu-container js-menu-container js-context-menu">
      <a href="#"
         class="minibutton bigger switcher js-menu-target js-commitish-button btn-branch repo-tree"
         data-hotkey="w"
         data-ref="master">
         <span><em class="mini-icon mini-icon-branch"></em><i>branch:</i> master</span>
      </a>

      <div class="context-pane commitish-context js-menu-content">
        <a href="#" class="close js-menu-close"><span class="mini-icon mini-icon-remove-close"></span></a>
        <div class="context-title">Switch branches/tags</div>
        <div class="context-body pane-selector commitish-selector js-navigation-container">
          <div class="filterbar">
            <input type="text" id="context-commitish-filter-field" class="js-navigation-enable js-filterable-field" placeholder="Filter branches/tags">
            <ul class="tabs">
              <li><a href="#" data-filter="branches" class="selected">Branches</a></li>
                <li><a href="#" data-filter="tags">Tags</a></li>
            </ul>
          </div>

          <div class="js-filter-tab js-filter-branches">
            <div data-filterable-for="context-commitish-filter-field" data-filterable-type=substring>
                <div class="commitish-item branch-commitish selector-item js-navigation-item js-navigation-target selected">
                  <span class="mini-icon mini-icon-confirm"></span>
                  <h4>
                      <a href="/ptbarthelemy/PSYCH204_Project/blob/master/paper/paper.tex" class="js-navigation-open" data-name="master" rel="nofollow">master</a>
                  </h4>
                </div>
            </div>
            <div class="no-results">Nothing to show</div>
          </div>

            <div class="js-filter-tab js-filter-tags filter-tab-empty" style="display:none">
              <div data-filterable-for="context-commitish-filter-field" data-filterable-type=substring>
              </div>
              <div class="no-results">Nothing to show</div>
            </div>
        </div>
      </div><!-- /.commitish-context-context -->
    </div>
  </div> <!-- /.scope -->

  <ul class="tabnav-tabs">
    <li><a href="/ptbarthelemy/PSYCH204_Project" class="selected tabnav-tab" highlight="repo_source">Files</a></li>
    <li><a href="/ptbarthelemy/PSYCH204_Project/commits/master" class="tabnav-tab" highlight="repo_commits">Commits</a></li>
    <li><a href="/ptbarthelemy/PSYCH204_Project/branches" class="tabnav-tab" highlight="repo_branches" rel="nofollow">Branches <span class="counter ">1</span></a></li>
  </ul>

</div>

          </div>
        </div><!-- /.repohead -->

        <div id="js-repo-pjax-container" class="container context-loader-container" data-pjax-container>

<!-- blob contrib key: blob_contributors:v21:2fd0485eaa95b9e1edea2e497c61e6f1 -->
<!-- blob contrib frag key: views10/v8/blob_contributors:v21:2fd0485eaa95b9e1edea2e497c61e6f1 -->

<div id="slider">

    <div class="frame-meta">

      <p title="This is a placeholder element" class="js-history-link-replace hidden"></p>
      <div class="breadcrumb">
        <span class='bold'><span itemscope="" itemtype="http://data-vocabulary.org/Breadcrumb"><a href="/ptbarthelemy/PSYCH204_Project" class="js-slide-to" data-direction="back" itemscope="url"><span itemprop="title">PSYCH204_Project</span></a></span></span> / <span itemscope="" itemtype="http://data-vocabulary.org/Breadcrumb"><a href="/ptbarthelemy/PSYCH204_Project/tree/master/paper" class="js-slide-to" data-direction="back" itemscope="url"><span itemprop="title">paper</span></a></span> / <strong class="final-path">paper.tex</strong> <span class="js-clippy mini-icon mini-icon-clippy " data-clipboard-text="paper/paper.tex" data-copied-hint="copied!" data-copy-hint="copy to clipboard"></span>
      </div>

      <a href="/ptbarthelemy/PSYCH204_Project/find/master" class="js-slide-to" data-hotkey="t" style="display:none">Show File Finder</a>

        <div class="commit commit-loader file-history-tease js-deferred-content" data-url="/ptbarthelemy/PSYCH204_Project/contributors/master/paper/paper.tex">
          Fetching contributors…

          <div class="participation">
            <p class="loader-loading"><img alt="Octocat-spinner-32-eaf2f5" height="16" src="https://a248.e.akamai.net/assets.github.com/images/spinners/octocat-spinner-32-EAF2F5.gif?1338945075" width="16" /></p>
            <p class="loader-error">Cannot retrieve contributors at this time</p>
          </div>
        </div>

    </div><!-- ./.frame-meta -->

    <div class="frames">
      <div class="frame" data-permalink-url="/ptbarthelemy/PSYCH204_Project/blob/4f0d202c1ba791661a94da0e3af58abe72221df3/paper/paper.tex" data-title="PSYCH204_Project/paper/paper.tex at master · ptbarthelemy/PSYCH204_Project · GitHub" data-type="blob">

        <div id="files" class="bubble">
          <div class="file">
            <div class="meta">
              <div class="info">
                <span class="icon"><b class="mini-icon mini-icon-text-file"></b></span>
                <span class="mode" title="File Mode">file</span>
                  <span>465 lines (347 sloc)</span>
                <span>30.783 kb</span>
              </div>
              <ul class="button-group actions">
                  <li>
                        <a class="grouped-button minibutton bigger lighter"
                           href="/ptbarthelemy/PSYCH204_Project/edit/master/paper/paper.tex"
                           data-method="post" rel="nofollow" data-hotkey="e">Edit</a>
                  </li>
                <li><a href="/ptbarthelemy/PSYCH204_Project/raw/master/paper/paper.tex" class="minibutton grouped-button bigger lighter" id="raw-url">Raw</a></li>
                  <li><a href="/ptbarthelemy/PSYCH204_Project/blame/master/paper/paper.tex" class="minibutton grouped-button bigger lighter">Blame</a></li>
                <li><a href="/ptbarthelemy/PSYCH204_Project/commits/master/paper/paper.tex" class="minibutton grouped-button bigger lighter" rel="nofollow">History</a></li>
              </ul>
            </div>
                <div class="data type-tex">
      <table cellpadding="0" cellspacing="0" class="lines">
        <tr>
          <td>
            <pre class="line_numbers"><span id="L1" rel="#L1">1</span>
<span id="L2" rel="#L2">2</span>
<span id="L3" rel="#L3">3</span>
<span id="L4" rel="#L4">4</span>
<span id="L5" rel="#L5">5</span>
<span id="L6" rel="#L6">6</span>
<span id="L7" rel="#L7">7</span>
<span id="L8" rel="#L8">8</span>
<span id="L9" rel="#L9">9</span>
<span id="L10" rel="#L10">10</span>
<span id="L11" rel="#L11">11</span>
